### 2014-07-22 MS.tex
~n

We are thankful to Mark Cornwall for help with the script to extend
MEDUSA to include phylogenetic uncertainty, Niklas Wahlberg for
commenting on the manuscript and giving us the posterior distribution of
trees, Luke Harmon for commenting on the manuscript and anonymous
reviewers for their comments, which greatly improved the manuscript,
Jessica Slove Davidson and Niklas Janz for access to their hostplant
data. The study was supported by a Kone Foundation grant (awarded to
Niklas Wahlberg), Finland (C. Peña) and the Research Council of Norway
(grant no. 204308 to M. Espeland). We acknowledge CSC--IT Center for
Science Ltd. (Finland) for the allocation of computational resources.

@@

2. Nyman T, Linder HP, Peña C, Malm T, Wahlberg N (2012) Climate-driven
diversity dynamics in plants and plant-feeding insects. Ecol Lett 15:
889--898.
doi:\href{http://dx.doi.org/10.1111/j.1461-0248.2012.01782.x}{10.1111/j.1461-0248.2012.01782.x}.

@@

7. Heikkilä M, Kaila L, Mutanen M, Peña C, Wahlberg N (2012) Cretaceous
origin and repeated tertiary diversification of the redefined
butterflies. P Roy Soc B 279: 1093--1099.
doi:\href{http://dx.doi.org/10.1098/rspb.2011.1430}{10.1098/rspb.2011.1430}.

@@

10. Wahlberg N, Leneveu J, Kodandaramaiah U, Peña C, Nylin S, et al.
(2009) Nymphalid butterflies diversify following near demise at the
Cretaceous/Tertiary boundary. P Roy Soc B 276: 4295--4302.
doi:\href{http://dx.doi.org/10.1098/rspb.2009.1303}{10.1098/rspb.2009.1303}.

11. Peña C, Wahlberg N (2008) Prehistorical climate change increased
diversification of a group of butterflies. Biol Lett 4: 274--278.
doi:\href{http://dx.doi.org/10.1098/rsbl.2008.0062}{10.1098/rsbl.2008.0062}.

12. Ferrer-Paris JR, S\'anchez-Mercado A, Viloria ÁL, Donaldson J (2013)
Congruence and Diversity of Butterfly-Host Plant Associations at Higher
Taxonomic Levels. PloS one 8: e63570.
doi:\href{http://dx.doi.org/0.1371/journal.pone.0063570}{0.1371/journal.pone.0063570}.

@@

17. Matos-Maraví PF, Peña C, Willmott KR, Freitas AV, Wahlberg N (2013)
Systematics and evolutionary history of butterflies in the ``Taygetis
clade'' (Nymphalidae: Satyrinae: Euptychiina): Towards a better
understanding of Neotropical biogeography. Mol Phylogenet Evol 66:
54--68.
doi:\href{http://dx.doi.org/10.1016/j.ympev.2012.09.005}{10.1016/j.ympev.2012.09.005}.

18. Brower AVZ, Wahlberg N, Ogawa JR, Boppré M, Vane-Wright RI (2010)
Phylogenetic relationships among genera of danaine butterflies
(Lepidoptera: Nymphalidae) as implied by morphology and DNA sequences.
Syst Biodivers 8: 75--89.
doi:\href{http://dx.doi.org/10.1080/14772001003626814}{10.1080/14772001003626814}.

@@

20. Kodandaramaiah U, Peña C, Braby MF, Grund R, Müller CJ, et al.
(2010) Phylogenetics of Coenonymphina (Nymphalidae: Satyrinae) and the
problem of rooting rapid radiations. Mol Phylogenet Evol 54: 386--394.
doi:\href{http://dx.doi.org/10.1016/j.ympev.2009.08.012}{10.1016/j.ympev.2009.08.012}.

@@

24. Peña C, Wahlberg N, Weingartner E, Kodandaramaiah U, Nylin S, et al.
(2006) Higher level phylogeny of Satyrinae butterflies (Lepidoptera:
Nymphalidae) based on DNA sequence data. Mol Phylogenet Evol 40: 29--49.
doi:\href{http://dx.doi.org/10.1016/j.ympev.2006.02.007}{10.1016/j.ympev.2006.02.007}.

@@

27. Peña C, Nylin S, Wahlberg N (2011) The radiation of Satyrini
butterflies (Nymphalidae: Satyrinae): a challenge for phylogenetic
methods. Zool J Linn Soc 161: 64--87.
doi:\href{http://dx.doi.org/10.1111/j.1096-3642.2009.00627.x}{10.1111/j.1096-3642.2009.00627.x}.

28. Peña C, Nylin S, Freitas AVL, Wahlberg N (2010) Biogeographic
history of the butterfly subtribe Euptychiina (Lepidoptera, Nymphalidae,
Satyrinae). Zool Scr 39: 243--258.
doi:\href{http://dx.doi.org/10.1111/j.1463-6409.2010.00421.x}{10.1111/j.1463-6409.2010.00421.x}.

@@

31. Beccaloni G, Viloria Á, Hall S, Robinson G (2008) Catalogue of the
hostplants of the Neotropical butterflies. London: The Natural History
Museum.

>>>>

We are thankful to Mark Cornwall for help with the script to extend
MEDUSA to include phylogenetic uncertainty, Niklas Wahlberg for
commenting on the manuscript and giving us the posterior distribution of
trees, Luke Harmon for commenting on the manuscript and anonymous
reviewers for their comments, which greatly improved the manuscript,
Jessica Slove Davidson and Niklas Janz for access to their hostplant
data. The study was supported by a Kone Foundation grant (awarded to
Niklas Wahlberg), Finland (C. Pe\~na) and the Research Council of Norway
(grant no. 204308 to M. Espeland). We acknowledge CSC--IT Center for
Science Ltd. (Finland) for the allocation of computational resources.

@@

2. Nyman T, Linder HP, Pe\~na C, Malm T, Wahlberg N (2012) Climate-driven
diversity dynamics in plants and plant-feeding insects. Ecol Lett 15:
889--898.
doi:\href{http://dx.doi.org/10.1111/j.1461-0248.2012.01782.x}{10.1111/j.1461-0248.2012.01782.x}.

@@

7. Heikkilä M, Kaila L, Mutanen M, Pe\~na C, Wahlberg N (2012) Cretaceous
origin and repeated tertiary diversification of the redefined
butterflies. P Roy Soc B 279: 1093--1099.
doi:\href{http://dx.doi.org/10.1098/rspb.2011.1430}{10.1098/rspb.2011.1430}.

@@

10. Wahlberg N, Leneveu J, Kodandaramaiah U, Pe\~na C, Nylin S, et al.
(2009) Nymphalid butterflies diversify following near demise at the
Cretaceous/Tertiary boundary. P Roy Soc B 276: 4295--4302.
doi:\href{http://dx.doi.org/10.1098/rspb.2009.1303}{10.1098/rspb.2009.1303}.

11. Pe\~na C, Wahlberg N (2008) Prehistorical climate change increased
diversification of a group of butterflies. Biol Lett 4: 274--278.
doi:\href{http://dx.doi.org/10.1098/rsbl.2008.0062}{10.1098/rsbl.2008.0062}.

12. Ferrer-Paris JR, S\'anchez-Mercado A, Viloria \'AL, Donaldson J (2013)
Congruence and Diversity of Butterfly-Host Plant Associations at Higher
Taxonomic Levels. PloS one 8: e63570.
doi:\href{http://dx.doi.org/0.1371/journal.pone.0063570}{0.1371/journal.pone.0063570}.

@@

17. Matos-Marav\'i PF, Pe\~na C, Willmott KR, Freitas AV, Wahlberg N (2013)
Systematics and evolutionary history of butterflies in the ``Taygetis
clade'' (Nymphalidae: Satyrinae: Euptychiina): Towards a better
understanding of Neotropical biogeography. Mol Phylogenet Evol 66:
54--68.
doi:\href{http://dx.doi.org/10.1016/j.ympev.2012.09.005}{10.1016/j.ympev.2012.09.005}.

18. Brower AVZ, Wahlberg N, Ogawa JR, Boppr\'e M, Vane-Wright RI (2010)
Phylogenetic relationships among genera of danaine butterflies
(Lepidoptera: Nymphalidae) as implied by morphology and DNA sequences.
Syst Biodivers 8: 75--89.
doi:\href{http://dx.doi.org/10.1080/14772001003626814}{10.1080/14772001003626814}.

@@

20. Kodandaramaiah U, Pe\~na C, Braby MF, Grund R, Müller CJ, et al.
(2010) Phylogenetics of Coenonymphina (Nymphalidae: Satyrinae) and the
problem of rooting rapid radiations. Mol Phylogenet Evol 54: 386--394.
doi:\href{http://dx.doi.org/10.1016/j.ympev.2009.08.012}{10.1016/j.ympev.2009.08.012}.

@@

24. Pe\~na C, Wahlberg N, Weingartner E, Kodandaramaiah U, Nylin S, et al.
(2006) Higher level phylogeny of Satyrinae butterflies (Lepidoptera:
Nymphalidae) based on DNA sequence data. Mol Phylogenet Evol 40: 29--49.
doi:\href{http://dx.doi.org/10.1016/j.ympev.2006.02.007}{10.1016/j.ympev.2006.02.007}.

@@

27. Pe\~na C, Nylin S, Wahlberg N (2011) The radiation of Satyrini
butterflies (Nymphalidae: Satyrinae): a challenge for phylogenetic
methods. Zool J Linn Soc 161: 64--87.
doi:\href{http://dx.doi.org/10.1111/j.1096-3642.2009.00627.x}{10.1111/j.1096-3642.2009.00627.x}.

28. Pe\~na C, Nylin S, Freitas AVL, Wahlberg N (2010) Biogeographic
history of the butterfly subtribe Euptychiina (Lepidoptera, Nymphalidae,
Satyrinae). Zool Scr 39: 243--258.
doi:\href{http://dx.doi.org/10.1111/j.1463-6409.2010.00421.x}{10.1111/j.1463-6409.2010.00421.x}.

@@

31. Beccaloni G, Viloria \'A, Hall S, Robinson G (2008) Catalogue of the
hostplants of the Neotropical butterflies. London: The Natural History
Museum.
